### 2016-06-28 thesis/mn.tex
figure

The remainder of this Chapter comprises the peer-reviewed version of the paper 
``Supermassive Black Holes and Their Host Spheroids. 
III. The $M_{\rm BH} - n_{\rm sph}$ correlation'' 
by G.~A.~D.~Savorgnan,  
accepted for publication in the \emph{The Astrophysical Journal}.

\includepdf[pages={1-10}]{ApJ2016b.pdf}

>>>>

The remainder of this Chapter comprises the published version of the paper 
``Supermassive Black Holes and Their Host Spheroids. 
III. The $M_{\rm BH} - n_{\rm sph}$ correlation'' 
by G.~A.~D.~Savorgnan,  
as it appears in Volume 821 of the \emph{The Astrophysical Journal}.

\includepdf[pages={1-8}]{ApJ2016b.pdf}

### 2016-06-28 thesis/publications.tex
figure

\item Shankar, F., Bernardi, M., Sheth, R.~K., Ferrarese, L., Graham, A.~W.,
      {\bf Savorgnan, G.~A.~D.}, Allevato, V., Marconi, A., Laesker, R., Lapi, A. \\
      Selection bias in dynamically-measured super-massive black hole samples: 
      its consequences and the quest for the most fundamental relation \\
      Submitted to \emph{MNRAS}. \\

>>>>

\item Shankar, F., Bernardi, M., Sheth, R.~K., Ferrarese, L., Graham, A.~W.,
      {\bf Savorgnan, G.~A.~D.}, Allevato, V., Marconi, A., Laesker, R., Lapi, A. \\
      Selection bias in dynamically-measured super-massive black hole samples: 
      its consequences and the quest for the most fundamental relation \\
      Accepted for publication in \emph{MNRAS}. \\
